\documentclass[10pt,journal,compsoc]{IEEEtran}


\usepackage[usenames,svgnames]{xcolor}
\usepackage[ruled,linesnumbered]{algorithm2e} 
\usepackage{graphicx}  
\usepackage{subfig} 
\usepackage{amsfonts}
\usepackage{ dsfont }
% \usepackage[colorlinks,linkcolor=blue]{hyperref} 
\usepackage{hyperref}
\hypersetup{colorlinks,allcolors=black}

\usepackage{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{url}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{bm}
\usepackage{pifont}
\usepackage{mydef}
\usepackage{threeparttable} 
\usepackage{ragged2e}
\usepackage[numbers]{natbib}
\usepackage{siunitx}
\usepackage[edges]{forest}

\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\newcommand\red[1]{{\color{red}{#1}}}
\newcommand{\figref}[1]{Figure~\ref{#1}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\secref}[1]{Section~\ref{#1}}
\renewcommand{\justify}{\leftskip=0pt \rightskip=0pt plus 0cm}


    
\begin{document}


\title{Graph Prompt Learning: A Comprehensive Survey and Beyond}


% \author{
% \IEEEauthorblockN{Xiangguo~Sun\IEEEauthorrefmark{1},  
% Jiawen Zhang\IEEEauthorrefmark{2}, 
% Xixi Wu\IEEEauthorrefmark{3},
% Hong~Cheng\IEEEauthorrefmark{1},
% Yun Xiong\IEEEauthorrefmark{3},
% Jia Li\IEEEauthorrefmark{2}
% } 
  
% \IEEEauthorblockA{
% \IEEEauthorrefmark{1}The Chinese University of Hong Kong, Hong Kong SAR.} \\
% \IEEEauthorblockA{\IEEEauthorrefmark{2}Hong Kong University of Science and Technology (Guangzhou), China.} \\
% \IEEEauthorblockA{\IEEEauthorrefmark{3}Fudan University, China} 
% }


 
% \author{Hao~Wu,
%         Sixu An,
%         Hong~Cheng,
%          Jia Li,
%          Xiangguo~Sun

% \IEEEcompsocitemizethanks{\IEEEcompsocthanksitem Xiangguo~Sun, Hong~Cheng: Department of Systems Engineering and Engineering Management, and Shun Hing Institute of Advanced Engineering, The Chinese University of Hong Kong, Hong Kong SAR.  \\\{xgsun, hcheng\}@se.cuhk.edu.hk

% \IEEEcompsocthanksitem Jiawen Zhang, Jia Li: Hong Kong University of Science and Technology (Guangzhou), China. \\jzhang302@connect.hkust-gz.edu.cn,jialee@ust.hk

% \IEEEcompsocthanksitem Xixi Wu, Yun Xiong: Shanghai Key Laboratory of Data Science, School of Computer Science, Fudan University, China. \\ 21210240043@m.fudan.edu.cn, yunx@fudan.edu.cn
% }
% }



% \markboth{IEEE TRANSACTIONS ON KNOWLEDGE AND DATA ENGINEERING}%
% \markboth{IEEE TRANSACTIONS}%
% {Xiangguo Sun \MakeLowercase{\textit{et al.}}: }



\IEEEtitleabstractindextext{
\begin{abstract}
\justify{Artificial General Intelligence (AGI) has transformed numerous fields, yet graph data remains comparatively less explored than text and vision in foundation-model-centered workflows. This survey reviews graph prompt learning from the perspective of cross-modality, cross-domain, and cross-task generalization, and organizes the area with a unified framework covering prompt tokens, token structures, and insertion patterns. We revisit the relationship between graph pre-training and prompting, discuss how prompts align downstream tasks with pretext objectives, and summarize representative prompt tuning strategies. Our taxonomy organizes over one hundred representative works, including recent studies through early 2026, across pre-training strategies, prompt design, multi-modal prompting, and graph domain adaptation. We also discuss ProG, a Python library for graph prompting, together with a companion repository for collecting relevant papers, benchmarks, and code resources. Finally, we outline current challenges and future directions to support continued research on graph prompting for graph representation learning and related AGI-oriented applications.
The companion website and ProG can be accessed by \url{https://github.com/WxxShirley/Awesome-Graph-Prompt} and \url{https://github.com/sheldonresearch/ProG}, respectively.
}

\end{abstract}

\begin{IEEEkeywords}
graph prompt, graph pre-training, graph learning, artificial general intelligence.
\end{IEEEkeywords}}



\maketitle





\input{1.intro} 
\input{2.methodology} 
\input{3.Preliminaries}
\input{4.Pre-training} 
\input{5} 
\input{6.Applications} 
\input{7.ProG}
\input{8.Discussion} 
\input{9.Conclusion}
\input{Ack}


\normalem % disable auto underline
\bibliographystyle{IEEEtranSN}
\bibliography{zotero.bib}
% \bibliography{080322.bib}
% \input{author}

\end{document}

