\section{Challenges and Future Directions}\label{sec:dis}
\subsection{Current Challenges}\label{sec:challenges}
Graph prompt learning has made significant research progress, moving from general benchmark tasks to more specialized settings and application scenarios. Nevertheless, the field still faces several challenges in model foundations, evaluation, applications, and transferability. In this subsection, we discuss these challenges in detail.

\textbf{Inherent Limitation within Graph Models} Prompts originate from the NLP field \cite{brown2020language, lester2021power, liu2023pretrain}, where pre-trained language models provide a relatively unified backbone and textual interface for adapting to downstream tasks. Graph prompt learning faces a different condition. Many graph prompts are not in-context prompts in the same sense as LLM prompts; they are often prompt tokens, prompt graphs, task templates, or structural adapters inserted into graph models. The main limitation is therefore not only the smaller scale of graph models, but also the lack of broadly reusable graph foundation models, unified graph-task interfaces, and sufficiently diverse pre-training corpora across domains. This makes it difficult to design prompts that can consistently activate transferable structural knowledge in the same way that textual prompts can elicit knowledge from large language models.


\textbf{Intuitive Evaluation of Graph Prompt Learning}
In the NLP field, prompts are typically in a discrete textual format \cite{brown2020language, robinson2023leveraging}, allowing for intuitive understanding, comparison, and explanation. Graph prompts, in contrast, are usually latent or model-internal. Early methods use learnable tokens \cite{sun2022gppt, fang2023universal, fang2022prompt, tan2023virtual, ma2023hetgpt} or augmented graphs \cite{sun2023all, huang2023prodigy, ge2023enhancing}, while newer designs further include semantic prompts, class prototypes, edge prompts, spectral prompts, and prompt selection mechanisms \cite{gong2024selfpro, ge2024psp, fu2025edge, yan2024igap, lv2025graphprompter}. These diverse forms make graph prompting more expressive, but they also make it harder to inspect what is being encoded by a prompt and how different prompt designs should be compared. As a result, evaluation still relies heavily on downstream accuracy, while intuitive measures of prompt quality, structural relevance, and cross-task robustness remain underdeveloped.


\textbf{More Downstream Applications}
Graph prompt learning is still largely evaluated on open-source benchmark tasks such as node and graph classification \cite{hamilton2017inductive, xu2018how}, but its application evidence is no longer limited to these settings. DyGPrompt \cite{yu2025dygprompt} extends graph prompting to dynamic interaction graphs, while GraphPro \cite{yang2024graphpro} and GPT4Rec \cite{zhang2024gpt4rec} apply temporal and multi-level prompts to recommender systems. In knowledge graph completion, APKGC \cite{maoliniyazi2026apkgc} and FFCL-KGC \cite{zhu2026ffclkgc} show that adaptive or dual prompts can improve structured relational prediction. Biomedical studies such as MOAT \cite{long2024moat}, DDIPrompt \cite{wang2024ddiprompt}, Prompt-DDG \cite{wu2024promptddg}, and protein multimer prompting \cite{gao2024protein} further demonstrate application evidence on molecular, drug-interaction, and protein-interaction graphs. However, this progress is uneven across domains. Recommendation and biomedical applications already provide relatively concrete evidence, whereas social-network security, industrial knowledge management, and other high-stakes settings still lack unified evaluation protocols and deployment-oriented studies. The key challenge is to build domain-specific pre-trained graph models and prompt designs that respect the structural, temporal, and semantic constraints of each application scenario.



\textbf{Transferable Prompt Designs} 
Transferability has become a central concern in graph prompt learning. Early studies \cite{liu2023graphprompt, sun2022gppt, gong2023prompt, fang2023universal, fang2022prompt, ge2023enhancing} often evaluate pre-training and prompt tuning within the same dataset or closely related tasks. PRODIGY \cite{huang2023prodigy} explores transferability within the same domain, and All in One \cite{sun2023all} provides empirical results regarding transferability across tasks and domains. More recent work further studies semantic alignment \cite{zhu2023graphcontrol}, structural alignment \cite{zhao2023graphglow}, universal prompting \cite{huang2025oneprompt}, cross-model prompt fusion \cite{he2026gp2f}, source-free graph domain adaptation \cite{zhang2024collaborate}, and multi-domain graph foundation models \cite{wang2025multidomain, yu2025samgpt}. Despite these advances, the field still lacks unified transfer protocols and diagnostic tools for explaining why a prompt succeeds in one graph domain but fails in another. Achieving reliable transferability requires joint consideration of task templates, semantic feature spaces, graph structural patterns, and pre-training data diversity.




\subsection{Future Directions}
With the above analysis on graph prompt, we summarize future directions as follows:

\textbf{Learning Knowledge from Graph Foundation Models.} Currently, graph models are still often tailored to specific domains or tasks, limiting their generalization abilities across broader domains \cite{liu2023graph, zhu2023graphcontrol}. A significant step toward graph foundation models has been taken by \citet{liu2023one}, whose OFA model addresses classification tasks for graphs from various domains by mapping graph features into a language-compatible space. Rather than replacing language-based interfaces, graph prompting can complement graph foundation models and graph-LLM interfaces by providing structure-aware, task-aware, and parameter-efficient adaptation mechanisms. Just as textual prompts adapt LLMs for diverse applications \cite{robinson2023leveraging, wang2023knowledge, brown2020language}, graph prompts may help graph foundation models expose task-specific knowledge while preserving graph topology and structural semantics. A promising direction is therefore to develop prompt interfaces that can work with both graph-native foundation models and graph-language models.


\textbf{Transferable Learning.} As discussed in Section \ref{sec:challenges}, graph prompt learning has begun to address transfer across tasks, domains, and pre-trained models, but a systematic understanding of transferability is still missing. Existing methods reformulate different tasks into unified templates \cite{sun2023all, huang2023prodigy}, align semantic features \cite{zhu2023graphcontrol}, or adapt structural patterns \cite{zhao2023graphglow}. More recent methods further consider universal prompts and cross-model adaptation \cite{huang2025oneprompt, he2026gp2f}. Future work should move beyond isolated transfer experiments toward standardized cross-dataset, cross-task, and cross-backbone evaluations. It is also important to characterize when a prompt transfers because it captures task semantics, graph structure, or pre-training distribution bias. Such diagnostics would make transferable graph prompting more reliable for heterogeneous, temporal, multi-domain, and application-specific graphs.




\textbf{More Theoretical Foundation.} Despite the success of graph prompt learning on various downstream tasks, many methods are still motivated by empirical analogies to prompt tuning in NLP \cite{liu2022ptuning, brown2020language, gao2021making, tsimpoukelli2021multimodal, qin2021learning, shin2020autoprompt}. Recent theoretical efforts have started to explain graph prompting from a graph-specific perspective. \citet{wang2025does} analyze graph prompts as data operations that approximate graph transformation operators, and derive error bounds for such operations under graph neural models. This view connects prompt insertion with graph augmentation, task reformulation, and upstream-downstream alignment. Nevertheless, the theoretical foundation remains incomplete. Future analysis should further explain how prompt forms interact with graph isomorphism, homophily and heterophily, structural distribution shifts, prompt capacity, and parameter efficiency. Specialized prompts for temporal, heterogeneous, molecular, or knowledge graphs may also require different assumptions from those used for general graph classification benchmarks.


\textbf{More Explainable and Understandable Design. }While existing graph prompt learning methods have demonstrated impressive results on various downstream tasks \cite{guo2023datacentric, wen2023voucher, yang2023empirical}, we still lack a clear understanding of what exactly is being learned from the prompts. The black-box learning mode of prompt vectors raises questions about their interpretability and whether we can establish meaningful correspondences between input data and the prompted graph \cite{sun2023all}. As prompt designs become more structural, explanations should go beyond visualizing prompt vectors and instead clarify how prompts correspond to nodes, edges, subgraphs, prototypes, temporal patterns, or geometric constraints \cite{gong2024selfpro, ge2024psp, fu2025edge, yan2024igap}. These issues are crucial for understanding and interpreting prompts but are still underexplored in graph prompt research. To work towards trustworthy graph prompt learning, it is promising to explore the self-interpretability \cite{dai2021selfexplainable}
% , zhang2021protgnn} 
to enable intuitive explanations of graph prompts. By gaining insights into the learned prompt vectors and structures, we can enhance our understanding of the underlying mechanisms and improve the interpretability of graph prompts. This, in turn, can lead to more effective utilization of prompts for high-stakes applications such as recommendation, biomedical modeling, security, and privacy-sensitive graph learning.