\section*{Acknowledgments}

The work was supported by grants from the Research Grant Council of the Hong Kong Special Administrative Region, China (Project No. CUHK 14217622), and CUHK Direct Grant No. 4055159. \dotuline{The first author, Dr. Xiangguo Sun, in particular, wants to thank his parents for their kind support during his tough period.} 

\noindent \textbf{Author Contributions:} 
\vspace*{-0.5\baselineskip} 
\begin{itemize}
    \item \textbf{Xiangguo Sun:} wrote section \ref{sec:intro}, section \ref{sec:method}, section \ref{subsec:why_prompt} (with Xixi), the main content of section \ref{sec:ptask}, section \ref{subsec:pmodal}, did proofreading of the whole paper, and proposed most of the original insights.
    \item \textbf{Jiawen Zhang:} wrote most of section \ref{sec:pre} (section \ref{subsec:notation}-\ref{subsec:his_prompt}), section \ref{sec:pretrain_method}, section \ref{sec:ptask}(collect, analyze papers and supplement insightful content), section \ref{sec:prog}, and were in charge of library development.
    \item \textbf{Xixi Wu:} wrote section \ref{subsec:why_prompt}, section \ref{sec:ptask} (collect, analyze papers and supplement insightful content), section \ref{sec:app}, most of section \ref{sec:dis} (challenges and future directions), collected and analyzed the references, and drew most of the figures.  
    \item \textbf{Hong Cheng,  Yun Xiong, and Jia Li:} were in charge of proofreading, and discussion, and contributed with many insightful opinions.
\end{itemize}