

\section{\jwxg{Prompting Methods for Graph Models}}
\label{sec:prompt}
\note{Jiawen help to find ``food'', and supplement anything insightful; Xiangguo writes the main content}

\red{
\textbf{[Miss WU 2/5] can help to collect papers, briefly discuss them, and writes the content}}




\subsection{Prompt Design for Graph Tasks}\label{subsec:ptask}
% \notee{I know it might be difficult, but I still expect you to help me collect more than 20 citations here! Because this subsection is the core part of the whole survey!}

\cite{anonymous2023one, anonymous2023when, chen2023exploring, chen2023ultradp, fang2023universal, fatemi2023talk, ge2023enhancing, gong2023prompt, guo2023datacentric, huang2023prodigy, li2023promptbased, liu2023graphprompt, liu2023one, ma2023hetgpt, sun2022gppt, tan2023virtual, wang2023knowledge, wen2023augmenting, wen2023prompt, yi2023contrastive, zhu2023graphcontrol, zhu2023sglpt}

\subsubsection{Graph Prompt for Node-level Tasks}\label{subsubsec:pnl}
\note{Let the readers know: (1) How do they design a prompt? (token, structure, inserting, answering, etc) (2) How do they reformulate downstream tasks to the pretext? (3) How do they learn or tune a prompt (4) pros and cons, briefly analyze the method to answer your research question (5) I also need to present a figure to better describe the workflow of prompting}

\notee{Try your best to find 5+ citations!}
\vspace*{\baselineskip} 

present (5) in front, then:

paragraph 1: (1) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc)  How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc) How do they design a prompt? (token, structure, inserting, answering, etc)

paragraph 2: (2)  How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? How do they reformulate downstream tasks to the pretext? \note{there are many detailed node-level tasks such as multi-class, multi-label, or other detailed application, you can split them by detailed tasks and present how they do that}

paragraph 3: (3) How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt  How do they learn or tune a prompt 

paragraph 4: (4) pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question  pros and cons, briefly analyze the method to answer your research question 

\subsubsection{Graph Prompt for Edge-level Tasks} \label{subsubsec:pel}
\note{Let the readers know: (1) How do they design a prompt? (2) How do they reformulate downstream tasks to the pretext?}

\notee{Try your best to find 5+ citations!}
\vspace*{\baselineskip} 



\subsubsection{Graph Prompt for Graph-level Tasks}\label{subsubsec:pgl}
\note{Let the readers know: (1) How do they design a prompt? (2) How do they reformulate downstream tasks to the pretext?}

\notee{Try your best to find 5+ citations!}
\vspace*{\baselineskip} 



\subsubsection{Multi-task Prompting}
\note{Let the readers know: (1) How do they design a prompt? (2) How do they reformulate downstream tasks to the pretext?}

\notee{Try your best to find 5+ citations! I recently found some work talking about using prompt in multi-task pre-training, and also some work using prompts in multi-task donstream}
\vspace*{\baselineskip} 




\input{5.1.5}






\subsection{Multi-modal Prompting using Graphs}\label{subsec:pmodal}

\note{TBD: this section can be also moved to the Application section}
% Jia Lee: 我在想，有没有可能把text-graph多模态的prompt也加进来，当然，这个点不是必须的。如果只是单模态graph，文献可能不够丰富
\notee{I think this section is not strictly focused on graph prompt, we can introduce multi-modal prompting using graphs. For example, some work might design text prompts or image prompts for fusing text-image modalities. and then they leverage graphs for better fusion, then we can also collect this paper in this section.}

\subsubsection{Text-Graph}
\notee{also include knowledge graph}

\subsubsection{More}

\notee{tell me more about multi-modal prompting using graph}



\subsection{Graph Domain Adaptation with Prompting}\label{subsec:pdomain}













\subsection{\red{Summary}}\label{subsec:discussion}
% \note{I will analyze the above work using our proposed framework: prompt tokens, token structure, inserting patterns} 


% \note{Here we also proposed an evaluated protocol to compare the flexibility of each graph prompt and present the results in a Table. To answer RQ3}
% In this survey, we will present how existing work on graph prompt try to solve the three foundation problems towards AGI as previously mentioned.  We offer this survey and wish to push forward the research area by answering the following key research questions (RQs):

% Cross domain, modalities, tasks